Gaze-dependent evidence accumulation predicts multi-alternative risky choice behaviour

### 2021-02-04 manuscript/main.tex
reran figure, fixed a wrong number in the manuscript

Finally, we investigated the ability of the best-performing model to predict individual differences in context effect strengths. Therefore, we predicted choices from the fitted GLA model and correlated the resulting RST with the observed data. Predicted RST correlated significantly with observed ones in attraction ($r$ = 0.72, HDI$_{95}$ = [0.62, 0.90], Figure \ref{fig:modelcomparison}i) and compromise ($r$ = 0.82, HDI$_{95}$ = [0.72, 0.92], Figure \ref{fig:modelcomparison}j) trials. However, the model underestimates large deviations from RST = 0.5, suggesting that its gaze-discount mechanism can capture the qualitative pattern of context effects but not their expression in participants with extreme RSTs.

>>>>

Finally, we investigated the ability of the best-performing model to predict individual differences in context effect strengths. Therefore, we predicted choices from the fitted GLA model and correlated the resulting RST with the observed data. Predicted RST correlated significantly with observed ones in attraction ($r$ = 0.76, HDI$_{95}$ = [0.62, 0.90], Figure \ref{fig:modelcomparison}i) and compromise ($r$ = 0.82, HDI$_{95}$ = [0.72, 0.92], Figure \ref{fig:modelcomparison}j) trials. However, the model underestimates large deviations from RST = 0.5, suggesting that its gaze-discount mechanism can capture the qualitative pattern of context effects but not their expression in participants with extreme RSTs.
